\ttitle

### 2015-06-03 Chapters/Introduction.tex
Impact of jaundice on renal physiology

@@

@@

\subsection{Jaundice and postoperative outcomes}
\subsection{Role of preoperative biliary drainage}

>>>>

%clarke_current_2006 - This is probably the best paper to base this entire section on.

@@

Several studies have reported that obstructive jaundice is associated with significant abnormalities in fluid homeostasis. Obstructive jaundice is associated with reduction in the interstitial volume as well as the circulating plasma volume.\parencite{sitges-serra_body_1992, padillo_preoperative_1999} In a study of 63 patients with obstructive jaundice, Padillo and co-workers reported that severity of jaundice, age of patient and reduced urinary sodium excretion were independently related to postoperative renal dysfunction. They also reported that these variables were related to abnormalities in the levels of hormones responsible for sodium and water homeostasis including atrial natriuretic peptide.\parencite{padillo_multivariate_2005} Endotoxemia consequent to lack of bile salts in the gut has also been postulated as a possible mechanism for renal dysfunction in patients with severe jaundice.\parencite{bailey_endotoxin_1976}

While expansion of the intravascular volume and avoiding dehydration by the judicious use of intravenous fluids has been recommended in avoiding renal dysfunction in jaundiced patients \parencite{parks_prospective_1994}, others have reported that relief of obstructive jaundice by restoring bile flow improves renal function independent of fluid therapy.\parencite{padillo_randomized_2005} Nonetheless, adequate perioperative fluid management, avoidance of hypotension, sepsis control and relief of obstructive jaundice play important roles in the prevention of renal failure in jaundiced patients.

@@

\subsection{Jaundice and postoperative outcomes}
\subsection{Role of preoperative biliary drainage}
%fang_pre-operative_2012 - Cochrane review
%wang_preoperative_2008 - Cochrane review
